Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-12-31 manuscript.tex
20161231

Recent scientific researches about deployments of the TSS focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}. Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the TSS. Iki et al. implemented the ground deployment experiment, and utilized the thruster to conduct the deployment of a kilometers-length electrodynamic tether from a special spool-type reel~\cite{iki2014experiments}. Aslanov et al. presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system was excited by a thruster force acting on the tug~\cite{aslanov2013dynamics}. Huang~et~al. investigated the attitude and deployment dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}. Jung et al. adopted the thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}. Liu et al. equipped the subsatellite with the thruster system, consisting of four pairs of thrusters, in order to regulate the attitude and deployment dynamics~\cite{liu2014attitude}. Zakrzhevskii divided the deployment process into two stages: in the first stage, the thruster was used to propel the subsatellite to the desired starting point of the next stage, and in the second stage, the tether was adjusted to the stable vertical configuration using tension generated by friction~\cite{zakrzhevskii2016method}. Mantellato et al. reported the thruster-aided deployment of tape tethers driven by both the tension and thruster forces~\cite{mantellato2015thrust}. These hybrid strategies has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, and thus is broadly utilized in engineering applications compared with other control strategies.

>>>>

Recent scientific researches about deployments of the TSS focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{zhu2008,kojima2015stabilisation,qi2016dynamics,zhong2016research,sun2013}. Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the TSS. Iki et al. implemented the ground deployment experiment, and utilized the thruster to conduct the deployment of a kilometers-length electrodynamic tether from a special spool-type reel~\cite{iki2014experiments}. Aslanov et al. presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system was excited by a thruster force acting on the tug~\cite{aslanov2013dynamics}. Huang~et~al. investigated the attitude and deployment dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}. Jung et al. adopted the thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}. Liu et al. equipped the subsatellite with the thruster system, consisting of four pairs of thrusters, in order to regulate the attitude and deployment dynamics~\cite{liu2014attitude}. Zakrzhevskii divided the deployment process into two stages: in the first stage, the thruster was used to propel the subsatellite to the desired starting point of the next stage, and in the second stage, the tether was adjusted to the stable vertical configuration using tension generated by friction~\cite{zakrzhevskii2016method}. Mantellato et al. reported the thruster-aided deployment of tape tethers driven by both the tension and thruster forces~\cite{mantellato2015thrust}. These hybrid strategies has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, and thus is broadly utilized in engineering applications compared with other control strategies.
